Value-Suppressing Uncertainty Maps

### 2017-03-31 paper/template.tex
Pdf changes

We performed a one-way ANOVA investigating the effect of chart type (juxtaposed, full bivariate, or VSUM) on accuracy. We found only a marginal effect $F(2,859) = 2.4$, $p=0.09$, although more trails with VSUMs were ($66\%$ of trials) compared to the other conditions ()

These results partially support our first hypothesis. While there

>>>>

We performed a one-way ANOVA investigating the effect of chart type (juxtaposed, full bivariate, or VSUM) on accuracy. We found only a marginal effect $F(2,859) = 2.4$, $p=0.09$, although VSUMs had the highest accuracy. Fig. X illustrates this result.

We also performed a one-way ANOVA on the effect of chart type on response time. In this case, we did find a significant main effect $(F,2,859) = 5.0$, $p<0.001$. A Tukey's test of Honest Significant Difference (HSD) found that participants were significantly slower at performing the task on juxtaposed maps, as opposed to the other map types.

These results partially support our first hypothesis.
